Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-07-18 main.tex
:construction: Update manuscript
:pencil: Update manuscript

	To the best of our knowledge, all existing \gls{sr} literatures assumed backscatter modulation employs either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a} or finite equiprobable inputs \cite{Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022,Hu2021a}.
	The former is impratical for passive nodes with constrained number of states, while the latter does not fully exploit \gls{csi} to boost achievable backscatter rate.
	Besides, most relevant designs \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} were built over ideal \gls{ml} or \gls{sic} receiver.
	However, the advantage of \gls{sic} is questionable because 1) it requires non-coherent primary encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver, 2) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 3) the backscatter symbol period is typically much longer due to physical constraints.
	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	Motivated by those, we propose the concept of Metascatter, which adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
	The contributions of this paper is summarized as follows.

	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{irs}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{irs}.
	When only considering backscatter performance, the distribution involves the highest entropy and Metacatter is essentially an \gls{ambc} node.

@@

	Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signal.
	As shown in Fig. \subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
	Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
	When illuminated, the node absorbs a portion of the impinging wave and scatters the remaining to the space.
	The absorbed signal can be used for information decoding and energy harvesting \cite{Kim2021a}, while the scattered signal is further decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
	Related to structure, shape and material of general objects, structural scattering consistently contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
	In contrast, antenna scattering models radiation pattern from antenna-load impedance mismatch, and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
	% The scatter model is illustrated in Fig. \subref*{fi:scatter_model}.
	Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ candidate states, and the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as%
	\footnote{It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.

@@

	\begin{figure}[!t]
		\centering
		\resizebox{\columnwidth}{!}{
			\includegraphics{assets/rate_region_2.eps}
		}
		\caption{Achievable rate regions by input-threshold design: Case II.}
		\label{fi:rate_region_2}
	\end{figure}
\end{section}

>>>>

	To the best of our knowledge, all existing \gls{sr} literatures assumed backscatter modulation employs either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a} or finite equiprobable inputs \cite{Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022,Hu2021a}.
	The former is impractical for passive nodes with constrained number of states, while the latter does not fully exploit \gls{csi} to boost achievable backscatter rate.
	Besides, most relevant designs \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} were built over ideal \gls{ml} or \gls{sic} receiver.
	However, the advantage of \gls{sic} is questionable because 1) it requires non-coherent primary encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver, 2) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 3) the backscatter symbol period is typically much longer due to physical constraints.
	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	Motivated by those, we propose the concept of Metascatter, which adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
	The contributions of this paper is summarized as follows.

	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{irs}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{irs}.
	When only considering backscatter performance, the distribution involves the highest entropy and Metascatter is essentially an \gls{ambc} node.

@@

	Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signal.
	As shown in Fig. \subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
	Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
	When illuminated, the node absorbs a portion of the impinging wave for information decoding and energy harvesting \cite{Kim2021a}, and scatters the remaining to the space. The scattered signal is further decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
	Depending on structure, shape and material of general objects, structural scattering consistently contributes to environment multipath and is covered by channel estimation \cite{Boyer2014}.
	In contrast, antenna scattering models radiation pattern from antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
	Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ reflection states, where the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as%
	\footnote{It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.

@@

	\begin{figure}[!t]
		\centering
		\resizebox{\columnwidth}{!}{
			\includegraphics{assets/rate_region_2.eps}
		}
		\caption{Achievable rate regions by input-threshold design: Case II.}
		\label{fi:rate_region_2}
	\end{figure}
	The parameters remain fixed unless specified.
\end{section}
